
  %-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Lucas Kim} \\ \vspace{1pt}
    \small  $|$ \href{mailto:lucas.kim2@uwaterloo.ca}{\underline{lucas.kim2@uwaterloo.ca}} $|$ 
    \href{https://lucaskamadakim.com}{\underline{lucaskamadakim.com}} $|$
    \href{https://github.com/Raptors65}{\underline{github.com/Raptors65}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {University of Waterloo}{N/A}
    {BSE, Software Engineering}{Sep. 2024 -- Present}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
        {Innovation Developer}{Jul. 2024 -- Aug. 2024}
        {Royal Bank of Canada}{Toronto, ON}
        \resumeItemListStart
          \resumeItem{Collaborated with an Agile team of 4 high school students to build and deploy a mortgage calculator using Angular, Spring Boot, Jenkins, and OpenShift 4.}
\resumeItem{Assisted over 180,000 clients in renewing their mortgages.}
\resumeItem{Presented the project to 100+ stakeholders, receiving recognition for technical excellence and presentation skills.}
        \resumeItemListEnd
\resumeSubheading
        {Tootor Website Manager}{May 2023 -- Sep. 2023}
        {NewArts Toronto}{Remote}
        \resumeItemListStart
          \resumeItem{Managed an online tutoring service with 60+ tutors and 500+ monthly tutoring sessions.}
\resumeItem{Integrated a GPT-3.5 AI tutor with output streaming, voice control, interactive activities, and function calling.}
\resumeItem{Ensured website accessibility by adjusting color contrast and metadata to comply with WCAG standards.}
\resumeItem{Led weekly meetings with a team of 20+ volunteers to discuss website improvements and new features.}
        \resumeItemListEnd
\resumeSubheading
        {Quality Assurance Analyst}{Jun. 2023 -- Aug. 2023}
        {GoalLine Solutions}{Burlington, ON}
        \resumeItemListStart
          \resumeItem{Conducted manual testing of functionality, user interface, and calculations to ensure adherence to client specifications.}
\resumeItem{Managed 200+ bug tickets on Azure DevOps, providing detailed reports with screenshots and reproduction steps.}
        \resumeItemListEnd
\resumeSubheading
        {Software Engineer Intern}{Feb. 2023 -- Jun. 2023}
        {North P\&D}{Toronto, ON}
        \resumeItemListStart
          \resumeItem{Submitted 10+ pull requests for the company website, including French translation integration with react-i18next.}
\resumeItem{Designed UI components for a client's website frontend using Webflow.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ShadeFindr} $|$ \emph{}}{N/A}
          \resumeItemListStart
            \resumeItem{Developed a navigation website to maximize shade for UV-sensitive individuals.}

\resumeItem{Won 1st place at CTRL+HACK+DEL, York University's first hackathon.}

          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, Python, Java, C, C++} \\
     \textbf{Frameworks}{: React, Next.js, Angular, Spring} \\
     \textbf{Developer Tools}{: Git, Docker, Jenkins, Figma} \\
     \textbf{Other}{: HTML, CSS, React Native, Tailwind CSS, Astro, AWS, Vercel, Azure DevOps, OpenShift 4, Supabase, OpenAI API, Agile Methodology, Web Content Accessibility Guidelines (WCAG), Bug Tracking, Client Communication, Team Leadership}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}

  